>

### 2025-09-22 docs/article.qmd
Finalize submission to GEPI

format:
  elsevier-pdf:
    keep-tex: true
    keep-md: true
    include-in-header:
      file: _header.tex
    journal:
      name: International Journal of Epidemiology
      formatting: review
      cite-style: numbername
      highlights:
        - Multi-class co-prescription was over ten times more common than same-class use in both antidepressant and anxiolytic users.
        - Seven highly central drug classes link psychiatric medications with chronic disease treatments, indicating key roles in co-prescription networks.
        - Network analysis reveals prescribing hubs not detectable through traditional drug utilization methods.
        - Findings align with Dutch clinical guidelines promoting multi-class use in anxiety and monotherapy in depression management.
        - Co-prescription patterns reflect underlying multimorbidity, highlighting the complexity of psychiatric and chronic illness care.
    output-file: iadb-network-analysis.pdf
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis.docx

@@

```{r fig-ssa}
#| fig-width: 16
#| fig-height: 12
#| fig-pos: H
#| fig-cap: Time-series decomposition of antidepressants dispensing data using singular spectrum analysis-based approach

@@

>>>>

format:
  elsevier-pdf:
    keep-tex: true
    keep-md: true
    include-in-header:
      - file: _header.tex
      - text: |
          \newpageafter{author}
    journal:
      name: Global Epidemiology
      formatting: review
      cite-style: numbername
      highlights:
        - Multi-class co-prescription was over ten times more common than same-class use in both antidepressant and anxiolytic users.
        - Seven highly central drug classes link psychiatric medications with chronic disease treatments, indicating key roles in co-prescription networks.
        - Network analysis reveals prescribing hubs not detectable through traditional drug utilization methods.
        - Findings align with Dutch clinical guidelines promoting multi-class use in anxiety and monotherapy in depression management.
        - Co-prescription patterns reflect underlying multimorbidity, highlighting the complexity of psychiatric and chronic illness care.
    output-file: iadb-network-analysis.pdf
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis.docx

@@

```{r fig-ssa}
#| fig-width: 16
#| fig-height: 12
#| fig-cap: Time-series decomposition of antidepressants dispensing data using singular spectrum analysis-based approach

@@

# Author Contributions {-}

**AL**: Conceptualization, Methodology, Formal analysis, Visualization, Writing - original draft, Project administration. **SB**: Methodology, Writing - review and editing. **EH**: Writing - review and editing. **JHB**: Data curation, Investigation, Project administration. **FJ**: Conceptualization, Supervision, Writing - original draft, Writing - review and editing. **TLF**: Conceptualization, Supervision, Methodology, Writing - original draft, Writing - review and editing.
